\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}

\title{LILT Validation Smoke (L1)}
\author{Validation Assets}
\date{}

\begin{document}
\maketitle

\begin{abstract}
This minimal article is the gold-standard Validation Asset for LILT continuous
verification. It exercises sectioning, labels, cross-references, inline math,
and environment pairing without scholarly package stacks.
\end{abstract}

\section{Structure and labels}
\label{sec:structure}

Sectioning and labels must survive sync and localization. See also
Section~\ref{sec:math} for an inline formula and the list below for paired
environments.

\begin{itemize}
  \item Prose segments are translation candidates.
  \item Markup structure is not free text for the model.
\end{itemize}

\section{Inline mathematics}
\label{sec:math}

A safe pipeline masks inline mathematics such as $E = mc^{2}$ before machine
translation and restores the same tokens afterward. Cross-reference integrity
is checked via Equation~\eqref{eq:toy} below.

% Display equation supports \eqref (CL-040) only — not display-math claim CL-061.
\begin{equation}
\label{eq:toy}
a + b = c
\end{equation}

Equation~\eqref{eq:toy} exists so that \texttt{\textbackslash eqref} and
\texttt{\textbackslash label} appear together with surrounding prose.

\section{Closing}
\label{sec:close}

If sync preserves namespaces, placeholders restore correctly after translate,
and fail-closed build behaves as documented, this smoke asset has done its job.

\end{document}
